Mega-analysis of the Interoceptive Accuracy Scale (IAS) Structure and its Subjective Correlates

### 2025-10-22 paper/1_Initial/manuscript.qmd
updated Results CFA

<!-- CFA Model Comparison -->
<!-- Name	BIC	RMSEA	Chi2	CFI	BF -->
<!-- fit_g	933909.6	0.124	27,249.398	0.783	Inf -->
<!-- fit_ega	1101773.3	0.035	2,306.303	0.984	NA -->
<!-- fit_egag	1106163.9	0.054	6,842.382	0.952	0 -->
<!-- fit_hclust	1112649.0	0.078	13,296.328	0.907	0 -->
<!-- fit_hclustg	1113829.4	0.078	14,528.732	0.898	0 -->
<!-- fit_efag	1115871.0	0.083	16,591.054	0.883	0 -->
<!-- fit_efa	1115871.0	0.083	16,591.054	0.883	0 -->

<!-- CFA -->
We then fitted and compared using CFA various candidate structures emerging from the previous analyses, including a 1-factor model (the G-model), a 3-factor model (EFA), a 3+1 model (EFA + general factor), a 5-factor model (HCA), a 5+1 model (HCA + general factor), a 7-factor model (EGA), and a 7+1 model (EGA + general factor). The EGA model with 7 factors of item pairs provided the best fit with the lowest RMSEA (0.035), lowest $\chi^2$ (2306.30), highest CFI (0.984). It was followed by the EGA + general factor model (RMSEA = 0.054, $\chi^2$ = 6842.38, CFI = 0.952), and the HCA model with 5 factors (RMSEA = 0.078, $\chi^2$ = 13296.33, CFI = 0.907). The other models performed poorly, with RMSEA > 0.08 and CFI < 0.90. The unique-factor model yielded the lowest BIC (which takes into account the number of factors), followed by the EGA model. All the other models displayed significantly (BIC-based Bayes Factor < 1/100) lower evidence compared to the EGA model.

This result was relatively consistent across unique datasets with the EGA model providing the best fit. In all samples where CFA converged, it showed excellent performance with low RMSEA (≈ 0.025–0.046), high CFI (≥ 0.97), and substantially lower $\chi^2$ compared to alternative models. Adding a general factor systematically worsened fit, while hierarchical clustering and EFA-based models showed poorer performance (RMSEA > 0.06, CFI < 0.93). Although BIC values occasionally favored alternative specifications, Bayes factor comparisons overwhelmingly supported the EGA solution, confirming its robustness across datasets.

@@

>>>>

<!-- CFA Model Comparison
Name	BIC	RMSEA	Chi2	CFI	BF
fit_g	13466.62	0.106	325.704	0.784	Inf
fit_ega	15870.94	0.026	72.825	0.988	NA
fit_egag	15892.96	0.059	180.403	0.924	1.654961e-05
fit_hclustg	15911.16	0.065	210.828	0.905	1.846821e-09
fit_hclust	15913.39	0.062	182.492	0.921	6.080789e-10
fit_efa	15941.59	0.073	253.472	0.877	4.576430e-16
fit_efag	15941.59	0.073	253.472	0.877	4.576430e-16 -->

<!-- Samples where CFA converged
fit_ega	15870.94	0.026	72.825	0.988	NA - sample 1a
fit_ega	28320.01	0.025	83.537	0.991	NA - sample 4
fit_ega	20224.33	0.046	130.586	0.978	NA - sample 6
it_ega	17647.14	0.038	98.571	0.973	NA - sample 7a
fit_ega	68203.78	0.033	178.485	0.982	NA - sample 7b
fit_ega	23336.33	0.036	102.630	0.976	NA - sample 7c
fit_ega	40816.35	0.033	128.727	0.976	NA - sample 8a
fit_ega	18031.48	0.031	83.225	0.977	NA - sample 8b
it_ega	720615.2	0.041	2,068.422	0.980	NA - sample 9
fit_ega	29023.36	0.052	181.784	0.948	NA - sample 11 
fit_ega	25899.23	0.038	116.734	0.977	NA - sample 13 
fit_ega	3975.352	0.040	65.620	0.975	NA - sampple 14 -->

@@

<!-- CFA -->
We then fitted and compared using CFA various candidate structures emerging from the previous analyses, including a 1-factor model (the G-model), a 3-factor model (EFA), a 3+1 model (EFA + general factor), a 5-factor model (HCA), a 5+1 model (HCA + general factor), a 7-factor model (EGA), and a 7+1 model (EGA + general factor). The EGA model with 7 factors of item pairs provided the best fit with the lowest RMSEA (0.026), lowest $\chi^2$ (72.825), highest CFI (0.988). It was followed by the EGA + general factor model (RMSEA = 0.059, $\chi^2$ = 180.403, CFI = 0.065), and the HCA model with 5 factors (RMSEA = 0.062, $\chi^2$ = 182.492, CFI = 0.921). The other models performed poorly, with RMSEA > 0.08 and CFI < 0.90. The unique-factor model yielded the lowest BIC (which takes into account the number of factors), followed by the EGA model. All the other models displayed significantly (BIC-based Bayes Factor < 1/100) lower evidence compared to the EGA model.

This result was relatively consistent across unique datasets with the EGA model providing the best fit. In all samples where CFA converged, it showed excellent performance with low RMSEA (≈ 0.025–0.052), high CFI (≥ 0.95), and substantially lower $\chi^2$ compared to alternative models. Adding a general factor systematically worsened fit, while hierarchical clustering and EFA-based models showed poorer performance (RMSEA > 0.05, CFI < 0.95). Although BIC values occasionally favored alternative specifications, Bayes factor comparisons overwhelmingly supported the EGA solution, confirming its robustness across datasets.
